---
title: "Julia's code for later usage?"
author: "Emily Morris"
date: "March 20, 2018"
output: html_document
---



```{r,message=FALSE, warning=FALSE}
#grouping by district and states
state_district<-house_elections %>%
  group_by(state,district)%>%
  summarise(gen_total=sum(general_votes),
            runoff_total=sum(runoff_votes), 
            primary_total = sum(primary_votes))
head(state_district, n=10)

#merge(joining state_district and house elections by both state and district)
vote_percent<-house_elections %>%
 merge(state_district, by = c("state","district")) %>%
  group_by(fec_id,ge_winner)%>%
  summarise(ratio=(general_votes/gen_total), 
            percent = (general_votes/gen_total)*100) #vote percentage got in general election for each candidate



```

```{r,message=FALSE, warning=FALSE}
 #filtering candidates to only be house and running in 2012
H_candidates_2012 <- candidates %>%
  filter(cand_office == "H",cand_election_yr==2012) %>%
  rename("candidate_name" = "cand_name") %>% 
  rename("fec_id" = "cand_id") #renaming cand_id to be fec_id so we can join 

 #summarise house candidates (total primary, total general votes, overall total votes)
percent_votes<-H_candidates_2012 %>%
 left_join(house_elections, by = "fec_id")%>%
   group_by(fec_id) %>%
summarize(Total_primary = sum(primary_votes), Total_general = sum(general_votes), total= Total_primary + Total_general)

candidates_2012 <- candidates %>%
  filter(cand_office == "H",cand_election_yr==2012) %>%
  rename("candidate_name" = "cand_name") %>% #renaming 
  rename("fec_id" = "cand_id") %>%
 full_join(percent_votes, by = "fec_id") 

candidates_2012_house<-candidates_2012%>%
  full_join(vote_percent, by = "fec_id")

#joining committees and contrabutions 
committees_contributions <- committees %>%
 full_join(contributions, by = "cmte_id")%>%
rename( "fec_id" ="cand_id.y")

#joining contrabutions and  2012 house candidates
contrabutions_candidates<-candidates_2012_house %>%
  left_join(committees_contributions, by = "fec_id")%>%
  group_by(candidate_name,cand_party_affiliation,cand_city,cand_office_district, fec_id, cand_office_state, Total_primary, Total_general,percent, total)%>%
  filter(cand_party_affiliation == "DEM"|cand_party_affiliation == "REP") %>% 
  mutate(transaction=sum(transaction_amt)) %>%
  filter(percent > 1 )

```


```{r,message=FALSE, warning=FALSE}
#grouping by state and district 
Data1<-contrabutions_candidates%>%
  group_by(cand_office_district, cand_office_state, transaction)%>%
  summarize(Total = sum(Total_general), 
            D = sum(ifelse(cand_party_affiliation == "DEM", Total_general, 0)), 
            R = sum(ifelse(cand_party_affiliation == "REP", Total_general , 0)), 
            Prop_dem = ((100*D)/Total), 
            Prop_R = ((100*R)/Total), 
            margin = abs(Prop_dem - Prop_R/Total))%>%
  mutate(winning_party = ifelse((Prop_dem > 50), "D", "R"))



# this function filters for state 
state_filter <-function(state_arg){Data1 %>%
    filter(cand_office_state == state_arg)}

# this function creates a ggplot where each dot is a district and the color is the party that won the district  and the size is the victory of margin and the x-axis = number of total ballots cast in each district and the y-axis = total amount of money spent in each district. 
plot_filter<-function(data_a){print(ggplot(data=data_a, aes(x=transaction, y =Total )) + 
  geom_point(aes(fill = winning_party, size = margin ), alpha=0.45, shape = 21, color="black", stroke = 1.29, position=position_dodge(width=0.7)) +
  scale_fill_manual(values = c("D" = "darkblue", "R" = "red"),"Party that won the district") +
    ggtitle(data_a$cand_office_state)+
    scale_y_continuous("Amount of Money Spent")+
  scale_x_continuous("Total ballots cast") +
    scale_size_continuous(range = c(1.725, 4.75),"Margin of Victoy(%)")+
    theme(axis.ticks.length = unit(4, "mm"), axis.ticks.y = element_blank()))}
     

#example:
plot_filter(state_filter("NJ"))
```

This is a scatterplot illustrating the relationship between Total ballots cast and Total number of Contributions per district in the 2012 House elections for the state of New Jersey. Each dot represents one district. The data points are organized on a Cartesian coordinate system. The y-axis (Total number of Contributions)  and the x-axis (Total ballots cast) both use a normal scale. The size of each dot is proportional to the margin of victory for the winner of the district (%), and the color of of each dot represents which candidate the district swung for; blue representing districts that the democratic candidate won and red representing districts that Republicans won. We can see that districts where more ballots were cast also had a larger amount of total contributions. The scatterplot shows that the districts where more ballots were cast ,this corresponds with the belief that higher voter turnout swings for the democratic candidate. We also saw that these districts are more likely to lean Democratic and have larger margins of victory and the more sparsely populated, the distirct the more likely it would vote Republican. However over all most districts in NJ  were won by democarts. We can also see that in New Jersey overall the districts that did swing for the Republican swung by smaller margins than districts that swung in favor of the Democrat. We were hoping that the margin of victory lined up with the money spent in the district but as we can see money spent in a district does not necessarily mean a close race. 

```{r, message=FALSE, warning=FALSE}
#plotting all states: 
lapply(lapply(Data1$cand_office_state,state_filter), plot_filter)
  
```
